Test susieI using whole genome, s40.22 samples

### 2020-12-11 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
susieI-rss

>>>>

##  Summary stats version
* The run setting is the same as  in "Select block + susieI (3)" except that we used summary statistics and in-sample LD as input.

```{r dirsSS}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20201001/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_rss_20201001/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_rss_20201001/"
```
```{r param1susieflSS, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config1.fl.susieIrssres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.fl.susieIrss.txt")

```{r pip1susieflSS, fig.height=6, fig.width=8}
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config1.flrerun.susieIrss.txt")
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP(low power)")
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)")
f3 <- ncausal_plot(susieIfs2[1:5], format = "susie", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "susie", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```
